A protocol \& event-sourced database for decentralized user-siloed data

### 2019-09-30 draft.tex
update date
Signed-off-by: andrew <andrew@textile.io>
adding Draft to page title
Signed-off-by: andrew <andrew@textile.io>
fix for carson
Signed-off-by: andrew <andrew@textile.io>

\title[Textile Threads]{A protocol \& event-sourced database for decentralized user-siloed data}
\author{Pick}
\author{Farmer}
\author{Sutula}
\affiliation{www.textile.io} \email{research@textile.io}
\author{?Gozalishivili others?}
\affiliation{other?} \email{research@textile.io}
\author{Hill}
\affiliation{www.textile.io} \email{contact@textile.io}

\shortauthors{www.textile.io}

\revised{18 September 2019}

@@

One of the most exciting aspects of user-siloed data is the the ability to build data-driven apps and services while users remain in control of their own data. Other projects have identified app-siloed data as a problem \cite{bernersLee_readwrite_2013,de_montjoye_trusted_2012}, and some have identified user-siloed data as a solution \cite{sambraSolidPlatformDecentralized2016}. However, none so far have addressed the problem of \emph{how data should be collected}, by providing a sufficiently interoperable protocol for scalable storage, transmission, and use of user-siloed application data.

>>>>

\title[Draft - Textile Threads]{A protocol \& event-sourced database for decentralized user-siloed data}
\author{Pick}
\author{Farmer}
\author{Sutula}
\affiliation{www.textile.io} \email{research@textile.io}
\author{?Gozalishivili others?}
\affiliation{other?} \email{research@textile.io}
\author{Hill}
\affiliation{www.textile.io} \email{contact@textile.io}

\shortauthors{draft - www.textile.io}

\revised{29 September 2019}

@@

One of the most exciting aspects of user-siloed data is the ability to build data-driven apps and services while users remain in control of their own data. Other projects have identified app-siloed data as a problem \cite{bernersLee_readwrite_2013,de_montjoye_trusted_2012}, and some have identified user-siloed data as a solution \cite{sambraSolidPlatformDecentralized2016}. However, none so far have addressed the problem of \emph{how data should be collected to make it extensible}, nor have they provided a sufficiently interoperable protocol for scalable storage, transmission, and use of user-siloed application data.
